Manuscript

### 2018-01-05 manuscript.Rmd
Cache manuscript during rmarkdown creation

```{r setup}
library(geojsonio)
library(leaflet)
library(tidyverse)
library(spdep)
library(maptools)
library(rgdal)
library(rgeos)
library(texreg)
library(leaflet)

>>>>

```{r setup, cache = FALSE, warning = FALSE, message = FALSE}
library(geojsonio)
library(leaflet)
library(tidyverse)
library(spdep)
library(maptools)
library(rgdal)
library(rgeos)
library(texreg)
library(leaflet)
